---
title: "Health Dynamics"
author: "Tagishi Mashego"
date: "2025-06-18"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
library(dplyr)

Health <- read_csv(here::here("data", "Health","HealthCare.csv")) 

code_files <- list.files(here::here("code"), pattern = "\\.R$", full.names = TRUE)
invisible(lapply(code_files, source))


```



# Introduction 

Ever heard the saying, "If you exercise more, you can eat whatever you want"? Yeah, now I'm over 200 pounds. 

# Impact of Physical Activity 

- Physical Activity alone does not cause weight loss 
- Indifference in weight change by activity level

```{r cars, echo=FALSE}

box_plot(data = Health)
```


# Regression Results 

```{r , echo=FALSE, message=FALSE, warning=FALSE}

 
library(knitr)
library(broom)
 model_object <- first_model(data = Health)
 
 tidy(model_object) %>%
   kable(
   digits = 3,
    caption = "Effect on Weight Change (lbs)"
   )
```

# Interpretation 
 
 
- Age is not a meaningful predictor of weight change , contrary to belief 
- Only sleep quality and stress levels are statistically significant predictors of weight change
- This model has a R-Squared Value of 0.55 , thus there are a lot of pivotal variables missing 




\newpage

# Sleep anyone ? 

```{r}

sleep_chart(data = Health)



```


# Conclusion 

Sure, the evidence on weight loss might be mixed , but I’m a big believer in the power of sleep. Sleep deprivation has been scientifically shown to impair neural pathways in the brain. So even if you’re not sleeping for your waistline, at least do it for your mind. 

