---
# IMPORTANT: Change settings here, but DO NOT change the spacing AT ALL.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Billionaires : Self-made or Daddy-made "
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Tagishi Mashego"  # First Author - note the thanks message displayed as an italic footnote of first page.
#Ref1: "Some Institution, Cape Town, South Africa" # First Author's Affiliation
#Email1: "nfkatzke\\@gmail.com" # First Author's Email address

#Author2: "John Smith"
#Ref2: "Some other Institution, Cape Town, South Africa"
#Email2: "John\\@gmail.com"
#CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.

#Author3: "John Doe"
#Email3: "Joe\\@gmail.com"

#CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
#keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
#JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.


if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


library(readr)
library(dplyr)
library(here)



# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.





```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->



# Introduction

You know what they say, the rich get richer. Let’s take a look at the wealth patterns in the world



## Part 1

<!-- The following is a code chunk. It must have its own unique name (after the r), or no name. After the comma follows commands for R which are self-explanatory. By default, the code and messages will not be printed in your pdf, just the output: -->

```{r Figure1, warning =  FALSE, fig.align = 'center', fig.cap = "Billionaire Comparison \\label{Figure1}", fig.height = 3, fig.width = 6, dev = 'png'}
  # This is just a random plot to show you a plot. This is done if the getwd() does not point to your Template's directory.
  # Set WD below to your project's working directory.


Billions <- read_csv(here::here("data", "Billions","billionaires.csv")) %>% arrange(desc(company.founded))

code_files <- list.files(here::here("code"), pattern = "\\.R$", full.names = TRUE)

invisible(lapply( list.files(here::here("code"), pattern = "\\.R$", full.names = TRUE),source))

firstplot(data = Billions , Title = "Billionaires : Inherited Wealth ( USA vs Rest of World") 


```

Kudos to the Americans , they have really created an economy that conducive for generating Uber wealth. Unfortunately, the notion held that those who are rich in America are only hard-nosed workaholics who built businesses from scratch, while the rest of the world's billionaires inherit their wealth , is simply not true. 


Figure \ref{Figure1} shows that the Rest of the World has more self-made billionaires than the USA, yes the rest of the world has more billionaires who have inherited that wealth too, but we see that both can be true. Surely one might surmise that this hold purely  based on the fact that the Rest of the World has more people than the USA , the next figure will address that thought. 


Table \ref{tab1} shows that over two-thirds of American billionaires over the history of time are self-made, dispelling any false notions that there is an entrepreneurial gene. Another noteworthy figure is the number of those who inherited via 5th generation or longer, as this family has been through depressions , recessions and  yet maintains billionaire status.

```{r ShortT, results = 'asis'}


library(dplyr)
library(xtable)


print(
  xtable(us_inheritance_table(data = Billions) , caption = "USA Billionaires by Inheritance Status \\label{tab1}"),
  include.rownames = FALSE,
  caption.placement = "bottom" , comment = FALSE ,
)




```

Looking at Table \ref{tab2} we see that the rest of the world has a slightly lower percentage of self-made billionaires at 63.8% . This is a narrative that the Americans are running with and I hate to be the one to confirm it. 


```{r , results = 'asis'}

library(dplyr)
library(xtable)



print(
  xtable(non_us_inheritance_table(data = Billions), caption = "Rest of the World by Inheritance Status\\label{tab2}"),
  include.rownames = FALSE,
  caption.placement = "bottom" , comment = FALSE 
)




```



\newpage

As quants we aim to steer our clients to invest in companies that are profitable.Table \ref{tab3} uses the number of billionaires associated with a company as a proxy for the profitability of the company , with 4 of the top 5 companies being US based it is no wonder the US is a certified  economic powerhouse.


```{r Sho, results = 'asis'}

library(dplyr)
library(xtable)

print(
  xtable(top5_companies_table(data = Billions) , caption = "Companies With Most Billionaires \\label{tab3}"),
  include.rownames = FALSE,
  caption.placement = "bottom" , comment = FALSE ,
)
    

```


## Part 2 


The year 2000 is widely regarded as the peak of the dot.com bubble  , a period where technology startups saw immense growth and profits. Unfortunately , it came to an end known as the bubble 'burst' in the early 2000, but does that mean incredibly successful tech startups are a thing of the past?


```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Companies founded Since 2000 \\label{Figure2}", fig.height = 3, fig.width = 6, dev = 'png'}



Billions <- read_csv(here::here("data", "Billions","billionaires.csv")) %>% arrange(desc(company.founded))

third_plot(data = Billions , Title = "Top 10 Sectors for Self-Made Billionaires ")


# Although the functions above are really simple, the principle is simple: containing calculations and data wrangling in their own functions will make this template much cleaner and more manageable.
# When you start working, delete these meaningless functions and replace with your own...

```


Figure \ref{Figure2} shows that the technology sector remains strong—ranking as the fourth most common source of billionaire-founded companies since 2000. However, it trails behind consumer services type sectors such as pharmaceuticals.




```{r ShortTable, include=FALSE, results='asis'}

library(xtable)
data <- mtcars[1:5,] %>% tibble::as_tibble()

table <- xtable(data, caption = "Short Table Example \\label{tab1}")
  print.xtable(table,
             # tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H',
             # scalebox = 0.3,
             comment = FALSE,
             caption.placement = 'bottom'
             )

```

```{r eval=FALSE, include=FALSE}
To reference calculations __in text__, _do this:_ From table \ref{tab1} we see the average value of mpg is `r mean(mtcars[1:5,]$mpg)`.

Including tables that span across pages, use the following (note that I add below the table: ``continue on the next page''). This is a neat way of splitting your table across a page.

Use the following default settings to build your own possibly long tables. Note that the following will fit on one page if it can, but cleanly spreads over multiple pages:
```



```{r LongTable, include=FALSE, results='asis'}

library(xtable)

data = mtcars %>% tibble::as_tibble()
  addtorow          <- list()
  addtorow$pos      <- list()
  addtorow$pos[[1]] <- c(0)
  addtorow$command  <- c(paste("\\hline \n",
                               "\\endhead \n",
                               "\\hline \n",
                               "{\\footnotesize Continued on next page} \n",
                               "\\endfoot \n",
                               "\\endlastfoot \n",sep=""))
table <- xtable(data, caption = "Long Table Example")
  print.xtable(table,
             tabular.environment = "longtable",
             floating = FALSE, # Leave this as is.
             table.placement = 'H', # Leave this as is.
             booktabs = T, # Aesthetics
             include.rownames = FALSE,  # Typically you don't want this in a table.
             add.to.row = addtorow, # For adding the Continued on next page part...
             comment = FALSE,
             caption.placement = 'top',  # Where do you want the caption?
             size="\\fontsize{12pt}{13pt}\\selectfont"  # Size of text in table..
             )
# See https://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf for table inspiration
```

\hfill

<!-- hfill can be used to create a space, like here between text and table. -->

```{r eval=FALSE, include=FALSE}
## Huxtable

Huxtable is a very nice package for making working with tables between Rmarkdown and Tex easier.

This cost some adjustment to the Tex templates to make it work, but it now works nicely.

See documentation for this package [here](https://hughjonesd.github.io/huxtable/huxtable.html). A particularly nice addition of this package is for making the printing of regression results a joy (see [here](https://hughjonesd.github.io/huxtable/huxtable.html#creating-a-regression-table)). Here follows an example:


If you are eager to use huxtable, comment out the Huxtable table in the Rmd template, and uncomment the colortbl package in your Rmd's root.

Note that I do not include this in the ordinary template, as some latex users have complained it breaks when they build their Rmds (especially those using tidytex - I don't have this problem as I have the full Miktex installed on mine). Up to you, but I strongly recommend installing the package manually and using huxtable. To make this work, uncomment the _Adding additional latex packages_ part in yaml at the top of the Rmd file. Then comment out the huxtable example in the template below this line. Reknit, and enjoy.
```



```{r include=FALSE, results='asis'}

if(!require(huxtable)) install.packages(huxtable)
library(huxtable)
data(diamonds, package = 'ggplot2')
Title <- "Regression Output"
Label <- "Reg01"
lm1 <- lm(price ~ carat, diamonds)
lm2 <- lm(price ~ depth, diamonds)
lm3 <- lm(price ~ carat + depth, diamonds)
htab <-
huxreg(lm1, lm2, lm3,
                statistics = c(N = "nobs", R2 = "r.squared"),
                note = "%stars%.") %>%
  set_caption(Title) %>%
  set_label(Label)
# More settings:
font_size(htab) <- 12
# Let's change regression names: this is slightly hacky, but works. Comment out this section to see what the default looks like:
  Names <- c( "Reg1", "Reg2", "Reg3")
  for(i in 1:length(Names)) {
    htab[1,][[1+i]] <- Names[i]
  }
# Now simply call the table:
htab

```






<!-- Make title of bibliography here: -->
<!-- \newpage -->



# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

 @Texevier 


